---
title: "Put a real title here"
subtitle: "SDS 192: MP2"
author: 
- name: Author One
  affiliation: Smith College
- name: Author Two
  affiliation: Smith College
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    theme: lumen
    df_print: paged
    code_folding: show
references:
- id: fec16
  type: manual
  title: "fec16: Data Package for the 2016 United States Federal Elections"
  author: 
  - family: Tapal
    given: Marium
  - family: Gahwagy
    given: Rana
  - family: Ryan
    given: Irene
  - family: Baumer
    given: Benjamin S.
  issued:
    year: 2020
  publisher: CRAN
  url: https://CRAN.R-project.org/package=fec16
  notes: "R package version 0.1.3"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = TRUE,
  warning = FALSE
)
library(tidyverse)
library(sds192)
```

## Introduction

What is this article about? 

This is how you make a footnote.[^github]

[^github]: Please see [our GitHub repository](https://github.com/sds192-i21/mp2-group-*) for complete code. 

You can cite references using parentheses or not. Sometimes you want to refer to the authors by name. 
For example, @fec16 provides the data. 
Other times, you want to cite something at the end of a sentence. 
Our analysis is based on data from the Federal Election Commission [@fec16].

If your data comes from a package, you can cite your data source using the information from the `citation()` function.

```{r}
citation("fec16")
```


## Loading the data

```{r, message=FALSE}
library(fec16)
```

To get the full `contributions` table, run this:

```{r, eval=FALSE}
contributions_all <- read_all_contributions()
```


## Some basic EDA

Here are some basic examples of what you can do.

- How many candidates running for what offices?

```{r}
candidates %>%
  group_by(cand_election_yr, cand_office, cand_office_st) %>%
  summarize(num_candidates = n()) %>%
  arrange(desc(num_candidates))
```

- How many committees [by type](https://classic.fec.gov/finance/disclosure/metadata/CommitteeTypeCodes.shtml)?

```{r}
committees %>%
  group_by(cmte_tp) %>%
  summarize(
    num_committees = n(), 
    cand_ids = sum(!is.na(cand_id))
  ) %>%
  arrange(desc(num_committees))
```

- What types of contributions are there and where do they go?

Remember that `contributions` is just a sample!

```{r}
contributions %>%
  group_by(entity_tp) %>%
  summarize(
    num_contributions = n(), 
    total_amount = sum(transaction_amt), 
    other_ids = sum(!is.na(other_id)),
    cand_ids = sum(!is.na(cand_id))
  ) %>%
  arrange(desc(num_contributions))
```

## Analysis

What did you discover?

## Conclusion

What did you learn about the 2016 federal election cycle?

## Word count

```{r word_count, message=FALSE, echo=FALSE}
text_stats()
```

## Standards

In this assignment, we attempted the following [standards](https://beanumber.github.io/sds192/standards.html):

- `r standard_button("wrangling")`: We met the Wrangling standard because we...
- `r standard_button("relational")`: We met the Relational standard because we...
- `r standard_button("reshape")`: We met the Reshape standard because we...
- `r standard_button("aesthetics")`: We mastered the Aesthetics standard because we...
- `r standard_button("markdown")`: We mastered the R Markdown standard because we...

## References
